### 2018-04-22 Sections/protocols_for_the_quantum_internet.tex
Ent pur, QoS, contigs
minor

@@

Mathematically, we are interested in the probability \mbox{$P(n_\text{meas}=n_\text{inc})$} that the measured number of photons ($n_\text{meas}$) matches the actual number of incident photons ($n_\text{inc}$). The structure of this expression will vary enormously depending on the details of the architecture (e.g multi-port interferometer vs fibre-loop). However, \cite{rohdeHuntington} presented a very general mathematical formalism applicable to all architectural variants. The simplest case to consider is the multi-port interferometer, owing to its perfect symmetry. The probability is simply the probability that no output mode from the multi-port contain multiple photons. A quick calculation yields,
\begin{align}
	P(n_\text{meas}=n_\text{inc}) = \binom{m}{n_\text{inc}}\left(\frac{1}{m}\right)^{n_\text{inc}},
\end{align}
not accounting for other errors such as losses or dark-counts.

>>>>

A completely general detector can be modelled as a POVM\index{POVM},
\begin{align}
\hat\Pi_m = \sum_{n=0}^\infty P(m|n) \ket{n}\bra{n},	
\end{align}
where $P(m|n)$ is the conditional probability of measuring $m$ photons given $n$ incident photons. The POVM is fully characterised by the conditional probabilities, which must be inferred from the specifics of the architecture. Alternately, a quantum process formalism can be constructed as,
\begin{align}
\mathcal{E}(\hat\rho) = \sum_{n=0}^\infty P(m|n) \hat{E}_n\hat\rho\hat{E}_n,	
\end{align}
where \mbox{$\hat{E}_n=\ket{n}\bra{n}$} are the Kraus operators\index{Kraus operators}.

@@

Mathematically, we are interested in the probability \mbox{$P(n_\text{meas}=n_\text{inc})$} that the measured number of photons ($n_\text{meas}$) matches the actual number of incident photons ($n_\text{inc}$). The structure of this expression will vary enormously depending on the details of the architecture (e.g multi-port interferometer vs fibre-loop). However, \cite{rohdeHuntington} presented a very general mathematical formalism applicable to all architectural variants. The simplest case to consider is the multi-port interferometer, owing to its perfect symmetry. The probability is simply the probability that no output mode from the multi-port contain multiple photons. A quick calculation yields,
\begin{align}
	P(n_\text{meas}=n_\text{inc}) = \binom{m}{n_\text{inc}}\left(\frac{\eta}{m}\right)^{n_\text{inc}},
\end{align}
not accounting for other lesser errors such as dark-counts.
